Tutorial_1

### 2024-07-22 Tutorial_1_descriptive_stats/Tutorial_1.Rmd
change neutral to blank

# create factor for condition (prime type)
data_wr <- data_wr %>% mutate(condition = condition + 1,
                              condition = factor(condition, levels = c(1,2,3), labels = c("neutral","congruent","incongruent")))
summary(data_wr)
```

@@

  data_medians <- tibble(period= data_median,
                         survival = rep(c(.5, 0),n_conditions),
                         condition = rep(1:n_conditions, each=2))
# plot the hazard functions
p1 <- df %>% ggplot(aes(x=period, color=condition, group=condition)) +
  geom_line(aes(y=hazard)) +
  geom_point(aes(y=hazard), size=1) + labs(color="Condition") +
  geom_linerange(aes(ymin=hazard-se_haz, ymax=hazard+se_haz), show.legend = F) +
  scale_x_continuous(breaks = c(0,1:(cutoff/binsize)), labels=c(0,1:(cutoff/binsize)*binsize),
                     limits = c(0,cutoff/binsize)) +
  scale_y_continuous(limits = c(0,haz_yaxis)) +
  labs(x="", y="h(t)", title = paste("Subject ", subj)) +
  theme(legend.background = element_rect(fill = "transparent"),
        panel.grid = element_blank(),
        legend.position = "top")
# plot the survivor functions
p2 <-df %>%
  ggplot(aes(x=period, color=condition, group=condition)) +
  geom_line(aes(y=survival), show.legend = F) +
  geom_point(aes(y=survival), size=1, show.legend = F) +
  geom_linerange(aes(ymin=survival-se_surv, ymax=survival+se_surv), show.legend = F) +
  # add vertical lines at the median RTs in the plot of the survivor functions using geom_path(). Make sure you apply the same levels and labels for the factor condition as above on line 83!
  geom_path(aes(x=period, y=survival, color=factor(condition, levels =c(1,2,3),labels=c("neutral","congruent","incongruent"))),
            data = data_medians, 
            linetype = 3, show.legend = F) +

@@

# view lifetable (column 7) for each condition for subject 1
pluck(data_final, 7, 1) %>% filter(condition=="neutral")
pluck(data_final, 7, 1) %>% filter(condition=="congruent")
pluck(data_final, 7, 1) %>% filter(condition=="incongruent")

>>>>

# create factor for condition (prime type)
data_wr <- data_wr %>% mutate(condition = condition + 1,
                              condition = factor(condition, levels = c(1,2,3), labels = c("blank","congruent","incongruent")))
summary(data_wr)
```

@@

  data_medians <- tibble(period= data_median,
                         survival = rep(c(.5, 0),n_conditions),
                         condition = rep(1:n_conditions, each=2))
# plot the hazard functions
p1 <- df %>% ggplot(aes(x=period, color=condition, group=condition)) +
  geom_line(aes(y=hazard)) +
  geom_point(aes(y=hazard), size=1) + labs(color="Condition") +
  geom_linerange(aes(ymin=hazard-se_haz, ymax=hazard+se_haz), show.legend = F) +
  scale_x_continuous(breaks = c(0,1:(cutoff/binsize)), labels=c(0,1:(cutoff/binsize)*binsize),
                     limits = c(0,cutoff/binsize)) +
  scale_y_continuous(limits = c(0,haz_yaxis)) +
  labs(x="", y="h(t)", title = paste("Subject ", subj)) +
  theme(legend.background = element_rect(fill = "transparent"),
        panel.grid = element_blank(),
        legend.position = "top")
# plot the survivor functions
p2 <-df %>%
  ggplot(aes(x=period, color=condition, group=condition)) +
  geom_line(aes(y=survival), show.legend = F) +
  geom_point(aes(y=survival), size=1, show.legend = F) +
  geom_linerange(aes(ymin=survival-se_surv, ymax=survival+se_surv), show.legend = F) +
  # add vertical lines at the median RTs in the plot of the survivor functions using geom_path(). Make sure you apply the same levels and labels for the factor condition as above on line 83!
  geom_path(aes(x=period, y=survival, color=factor(condition, levels =c(1,2,3),labels=c("blank","congruent","incongruent"))),
            data = data_medians, 
            linetype = 3, show.legend = F) +

@@

# view lifetable (column 7) for each condition for subject 1
pluck(data_final, 7, 1) %>% filter(condition=="blank")
pluck(data_final, 7, 1) %>% filter(condition=="congruent")
pluck(data_final, 7, 1) %>% filter(condition=="incongruent")
